---
title: "Recruitment"
author: 
date: "Last Updated: 8/25/2020"
output: 
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
---
```{r load-packages, echo=FALSE, warning=FALSE, include=FALSE, cache=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(knitr)
options(digits=1)
library(ggpubr)
library(plotly)
library(emmeans)
library(papaja)
library(ggpubr)
library(kableExtra)
library(descr)
library(dplyr)
library(magick)
library(tidyverse)
library(ggformula)
library(lubridate)
library(janitor)
library(plyr)
library(tigerstats)
library(plotrix)
library(RColorBrewer)
options(knitr.table.format = "html", knitr.kable.NA = '') 
```

```{r Family Statuses, echo = FALSE, message=FALSE}
#DK Data

FamData <- read_excel("~/Dropbox (University of Oregon)/SEAL R01/_Remote SEAL Pilot/Project Management/FamTracker.xlsx")

IntroDate <- as.Date(FamData$`Intro Call Date`, format = "%m/%d/%Y")
#FinishSurveys <- as.Date(FamData$`Finished Surveys`, format = "%m/%d/%Y")
#LENARec <- as.Date(FamData$`LENAs recieved`, format = "%m/%d/%Y")
LENARet <- as.Date(FamData$`LENAs Returned`, format = "%m/%d/%Y")



#SurvComp <- as.data.frame(table(FinishSurveys))
#LENARec <- as.data.frame(table(LENARec))
LENARet <- as.data.frame(table(LENARet))
```


```{r DK Log variable setup, echo = FALSE, message=FALSE}
#DK Data
DKdata <- read.csv(file = '/Volumes/psy-ctn/psy-ctn/SNAPLab/SNAP Projects/SEAL/00_rSEAL/02_rSEAL_Data/Wave_1/RedCap/DK_Log/rSEALDKLOG_25AUG2020.csv')

Atempt1Date <- as.Date(DKdata$rseal_dklog_026, format = "%m/%d/%Y")
Atempt2Date <- as.Date(DKdata$rseal_dklog_029, format = "%m/%d/%Y")
Atempt3Date <- as.Date(DKdata$rseal_dklog_032, format = "%m/%d/%Y")

DKParsedData <- select (DKdata, rseal_dkid,rseal_dklog_006:rseal_dk_log_complete )
DKParsedData <- as_tibble(DKParsedData)

```


```{r recruitment, echo=FALSE, message=FALSE, warning=FALSE}

Scheduled <-subset(DKParsedData,DKParsedData$rseal_dklog_025 == '4' | DKParsedData$rseal_dklog_028 == '4'| DKParsedData$rseal_dklog_031 == '4' )

ScheduledCount <- nrow(Scheduled)

#Number in DK Log compared to how many contacted so far

#Contacted <- subset(DKParsedData, DKParsedData$rseal_dklog_009 == '1' | DKParsedData$rseal_dklog_009 == '0')

#ToContact <- sum(nrow(DKParsedData) - nrow(Contacted))

#Relative success rate (Number interested)

Interested <- subset(DKParsedData, DKParsedData$rseal_dklog_009 == '1')
Interested <- nrow(Interested)

ToSched <- Interested - ScheduledCount

NumInterested <-nrow(Interested)


AttemptContact <-subset(DKParsedData,
DKParsedData$rseal_dklog_025 == '1' | DKParsedData$rseal_dklog_025 == '2' | DKParsedData$rseal_dklog_025 == '3' | DKParsedData$rseal_dklog_025 == '4' | DKParsedData$rseal_dklog_025 == '5' | DKParsedData$rseal_dklog_025 == '6' | DKParsedData$rseal_dklog_028 == '1'| DKParsedData$rseal_dklog_028 == '2'| DKParsedData$rseal_dklog_028 == '3'| DKParsedData$rseal_dklog_028 == '4'| DKParsedData$rseal_dklog_028 == '5'| DKParsedData$rseal_dklog_028 == '6'| DKParsedData$rseal_dklog_031 == '1'| DKParsedData$rseal_dklog_031 == '2'| DKParsedData$rseal_dklog_031 == '3'| DKParsedData$rseal_dklog_031 == '4'| DKParsedData$rseal_dklog_031 == '5'| DKParsedData$rseal_dklog_031 == '6' )
AttemptContact2 <- nrow(AttemptContact)

ToContact <- sum(nrow(DKParsedData) - AttemptContact2)

PercentInterested <- 100*sum(Interested, na.rm=T)/AttemptContact2

SchedSuccess <-100*sum(ScheduledCount)/AttemptContact2

TotalDK <- nrow(DKParsedData)
ToCall <- TotalDK-AttemptContact2


#DHS PercentInterested and scheduling success rate

DHSsubset <- subset(DKParsedData, DKParsedData$rseal_dklog_006 == '2')
DHSCount <- nrow(DHSsubset)

DHSInterested <- subset(DHSsubset, DHSsubset$rseal_dklog_009 == '1')
DHSInterested <- nrow(DHSInterested)

DHSScheduled <-subset(DHSsubset,DHSsubset$rseal_dklog_025 == '4' | DHSsubset$rseal_dklog_028 == '4'| DHSsubset$rseal_dklog_031 == '4' )

DHSScheduledCount <- nrow(DHSScheduled)

DHSContacted <- AttemptContact <-subset(DHSsubset,
DHSsubset$rseal_dklog_025 == '1' | DHSsubset$rseal_dklog_025 == '2' | DHSsubset$rseal_dklog_025 == '3' | DHSsubset$rseal_dklog_025 == '4' | DHSsubset$rseal_dklog_025 == '5' | DHSsubset$rseal_dklog_025 == '6' | DHSsubset$rseal_dklog_028 == '1'| DHSsubset$rseal_dklog_028 == '2'| DHSsubset$rseal_dklog_028 == '3'| DHSsubset$rseal_dklog_028 == '4'| DHSsubset$rseal_dklog_028 == '5'| DHSsubset$rseal_dklog_028 == '6'| DHSsubset$rseal_dklog_031 == '1'| DHSsubset$rseal_dklog_031 == '2'| DHSsubset$rseal_dklog_031 == '3'| DHSsubset$rseal_dklog_031 == '4'| DHSsubset$rseal_dklog_031 == '5'| DHSsubset$rseal_dklog_031 == '6' )

DHSContacted <- nrow(DHSContacted)

DHSPercentInterested <- 100*DHSInterested/DHSContacted

DHSSchedSuccess <-100*DHSScheduledCount/DHSContacted

```
The qualtrics dashboard which shows how many many surveys are complete by participant can be accessed here: https://ql.tc/UFAErS

<font size = "4"> There are currently <font size="4" color="red"> **`r papaja::printnum(ScheduledCount)`**</font> participants scheduled for (or have completed) their Wave 1 phone call, with a <font size="4" color="red"> **`r papaja::printnum(SchedSuccess)`\%**</font> scheduling success rate (number scheduled out of total contacted).</font>

<font size = "4"> There are currently <font size="4" color="red"> **`r papaja::printnum(Interested)`**</font> participants who are interested, with <font size="4" color="red"> **`r papaja::printnum(ToSched)`**</font> who still need to be scheduled.</font> 

<font size = "4"> Of those who were contacted, <font size="4" color="red"> **`r papaja::printnum(PercentInterested)`\%**</font> were interested, and there are currently <font size="4" color="red"> **`r ToContact`**</font> participants whose interest in participating has not been determined yet.</font> 

<font size = "4"> There are <font size="4" color="red"> **`r papaja::printnum(AttemptContact2)`**</font> participants who have been contacted, and <font size="4" color="red"> **`r papaja::printnum(ToCall)`**</font> who still need to be contacted.</font> 


<font size = "4"> So far, there are <font size="4" color="red"> **`r papaja::printnum(DHSCount)`**</font> potential participants from DHS Mailer, <font size="4" color="red"> **`r papaja::printnum(DHSContacted)`**</font> of whom have been contacted. Of those who were contacted, <font size="4" color="red"> **`r papaja::printnum(DHSInterested)` (`r papaja::printnum(DHSPercentInterested)`\%)**</font> participants showed interest and <font size="4" color="red"> **`r papaja::printnum(DHSScheduledCount)` (`r papaja::printnum(DHSSchedSuccess)`\%)**</font> participants got scheduled successfully.</font>

``` {r Form Counts, fig.width=4, fig.height=4, echo = FALSE, message=FALSE}

Form2 <- table(DKParsedData$rseal_dk_log_complete)
FormPlot <- barplot(Form2, beside = TRUE, main = "Form Statuses",
        col = brewer.pal(3,"Set2"), 
        xlab = " ",
        ylab = "Count", legend = c("Ineligible or Not Interested", "Still Calling","Scheduled"),
        args.legend = list(x="topright", cex=.7),ylim=c(0,110), xaxt = "n")
barlabels(FormPlot, Form2)

```  


```{r Attempt Status, fig.width=4, fig.height=4, echo = FALSE, message=FALSE}

#Counts of Statuses

Introcall <- table(FamData$`Finished Intro Call`)
StatusPlot <- barplot(Introcall, beside = TRUE, main = "Intro Call Statuses",
        col = brewer.pal(4,"Set2"), 
        xlab = " ",
        ylab = "Count", legend = c("Complete", "Dropout", "Scheduled", "Potential Dropout"),
        args.legend = list(x="topright", cex=.7),ylim=c(0,20), xaxt = "n")
barlabels(StatusPlot, Introcall)


#Attempt Statuses

Attempt1 <- table(DKParsedData$rseal_dklog_025)
Attempt1Plot <- barplot(Attempt1, beside = TRUE, main = "Attempt 1 Statuses",
        col = brewer.pal(6,"Set2"), 
        xlab = " ",
        ylab = "Count", legend = c("Contact family","Requested Call Back", "Non-responsive/Disconnected", "Scheduled", "Not Interested", "Ineligible"),
        args.legend = list(x="topright", cex=.7),ylim=c(0,80), xaxt = "n")
barlabels(Attempt1Plot, Attempt1)

Attempt2 <- table(DKParsedData$rseal_dklog_028)
Attempt2Plot <- barplot(Attempt2,
        col = brewer.pal(6,"Set2"), 
        main = "Attempt 2 Statuses",
        xlab = " ",
        ylab = "Count", legend = c("Contact family","Requested Call Back", "Non-responsive/Disconnected", "Scheduled", "Not Interested", "Ineligible"),
        args.legend = list(x="topright", cex=.7), ylim=c(0,40),
        xaxt = "n")
barlabels(Attempt2Plot, Attempt2)

Attempt3 <- table(DKParsedData$rseal_dklog_031)
Attempt3Plot <- barplot(Attempt3, beside = TRUE, main = "Attempt 3 Statuses",
        col = brewer.pal(4,"Set2"), 
         xlab = " ",
        ylab = "Count", legend = c( "Non-responsive/Disconnected", "Scheduled", "Not Interested", "Ineligible"),
         args.legend = list(x="topright", cex=.7),ylim=c(0,10), xaxt = "n")
barlabels(Attempt3Plot, Attempt3)

```   
```{r Not Interested Setup, fig.width=4, fig.height=4, echo = FALSE, message=FALSE}

#Not Interested Reasons

NotInt <- subset(DKParsedData,
                   DKParsedData$rseal_dklog_010___0 == '1' |
                   DKParsedData$rseal_dklog_010___1 == '1'| 
                   DKParsedData$rseal_dklog_010___2 == '1' |
                   DKParsedData$rseal_dklog_010___3 == '1'| 
                   DKParsedData$rseal_dklog_010___4 == '1' |
                   DKParsedData$rseal_dklog_010___5 == '1' |
                   DKParsedData$rseal_dklog_010___6 == '1' |
                   DKParsedData$rseal_dklog_010___7 == '1' |
                   DKParsedData$rseal_dklog_010___8 == '1'|
                   DKParsedData$rseal_dklog_010___9 == '1')

NotInt2 <- dplyr::select (NotInt, rseal_dklog_010___0,rseal_dklog_010___1,rseal_dklog_010___2,rseal_dklog_010___3,rseal_dklog_010___4,rseal_dklog_010___5,rseal_dklog_010___6,rseal_dklog_010___7,rseal_dklog_010___8,rseal_dklog_010___9 )

NotInt3<- t(NotInt2)
rownames(NotInt3) <- c("Unknown", "Time Commitment","Too Stressed","Don't need help / Not a good fit for family","Privacy Concerns","Out of my comfort zone","Cultural / Language Barriers","I do not understand the project","I do not know the staff","Other")
```   

<font size = "4"> **Counts and reasons given by those not interested in participating.**</font> 

``` {r Not Interested Reasons, fig.width=4, fig.height=4, echo = FALSE, message=FALSE}

kable(NotInt3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```  
